No early warning signals for stochastic transitions: insights from large deviation theory

### 2013-06-13 inst/doc/CommentReply.tex
line wrap, add dryad DOI

\begin{figure}[htbp]
\centering
\includegraphics{Figure1.pdf}
\caption{Figure 1. Histogram shows the frequency the correlation
statistic $\tau$ observed for each warning signal (variance,
autocorrelation coefficient) on the large deviation samples from each
model. Background distribution of all samples show by smooth line
(kernel density estimate). More positive values of tau are supposed to
indicate a rising indicator which can be a signal of an approaching
transition {[}2{]}. The OU model uses $\alpha = 5$, $\sigma=3.5$,
$t \in (0, 10)$, 2000 replicates, 20,000 sample points each.
Conditionally selected trajectories experiencing a deviation of at least
-4, and analyzed the 1,500 data points prior to the threshold to
determine a warning signal (following Reference 5). (Code at:
https://raw.github.com/cboettig/earlywarning/resubmission/inst/doc/Figure1.Rmd,
data at:
https://raw.github.com/cboettig/earlywarning/resubmission/inst/doc/Figure1.csv}
\end{figure}

@@

The authors acknowledge the generous support of NSF grant to AH and
helpful comments from TA Perkins, as well as the reviews from an
anonymous reviewer and P. Ditlevsen.

>>>>

\begin{figure}[htbp]
\centering
\includegraphics{Figure1.pdf}
\caption{Figure 1. Histogram shows the frequency the correlation
statistic $\tau$ observed for each warning signal (variance,
autocorrelation coefficient) on the large deviation samples from each
model. Background distribution of all samples show by smooth line
(kernel density estimate). More positive values of tau are supposed to
indicate a rising indicator which can be a signal of an approaching
transition {[}2{]}. The OU model uses $\alpha = 5$, $\sigma=3.5$,
$t \in (0, 10)$, 2000 replicates, 20,000 sample points each.
Conditionally selected trajectories experiencing a deviation of at least
-4, and analyzed the 1,500 data points prior to the threshold to
determine a warning signal (following Reference 5). (Code at:
https://raw.github.com/cboettig/earlywarning/resubmission/inst/doc/Figure1.Rmd,
data at:
https://raw.github.com/cboettig/earlywarning/resubmission/inst/doc/Figure1.csv
(these links should be replaced with the appropriate citation to Dryad,
where these files are now deposited under provisional DOI:
10.5061/dryad.1dj62)}
\end{figure}

@@

The authors acknowledge the generous support of NSF grant EF 0742674 to
AH and helpful comments from TA Perkins, an anonymous reviewer and
reviewer P. Ditlevsen.
